\Large\bf FlexibleSUSY --- A spectrum generator generator for supersymmetric models

### 2014-06-12 doc/flexiblesusy-paper.tex
added more references to non-decoupled D-term approach, citing the kaplan paper. and Anibal Medina's paper.  there are probably many more.

These developments motivate the exploration of non-minimal SUSY models
which ameliorate the naturalness problems, as can happen in the \ESSM
\cite{King:2005jy,King:2005my,King:2007uj,Athron:2010zz} and USSM
\cite{Fayet:1977yc,Suematsu:1994qm,Cvetic:1995rj,deCarlos:1997yv,Cvetic:1997ky,Demir:1998dk,Langacker:1998tc,Erler:2002pr,Choi:2006fz,Ham:2007wc,Langacker:2008yv,Ham:2008xf,Kalinowski:2008iq,Bharucha:2013ela}
by raising the tree level Higgs mass. At the same time they can also
motivate models that are developed with a fresh perspective, based on
other considerations.  In both cases exploration of such models can be
aided if it is possible to quickly create a fast spectrum generator.
Currently there is only one option for this, a SPheno-like FORTRAN
code which can be generated from \sarah
\cite{Staub:2010ty,Staub:2009bi,Staub:2010jh,Staub:2012pb,Staub:2013tta}.

@@

%\cite{Kalinowski:2008iq}
\bibitem{Kalinowski:2008iq} 
  J.~Kalinowski, S.~F.~King and J.~P.~Roberts,
  %``Neutralino Dark Matter in the USSM,''
  JHEP {\bf 0901}, 066 (2009)
  [arXiv:0811.2204 [hep-ph]].
  %%CITATION = ARXIV:0811.2204;%%
  %30 citations counted in INSPIRE as of 09 Jun 2014
%\cite{Bharucha:2013ela}
\bibitem{Bharucha:2013ela} 
  A.~Bharucha, A.~Goudelis and M.~McGarrie,
  %``En-gauging Naturalness,''
  arXiv:1310.4500 [hep-ph].
  %%CITATION = ARXIV:1310.4500;%%
  %9 citations counted in INSPIRE as of 12 Jun 2014

>>>>

These developments motivate the exploration of non-minimal SUSY models
which ameliorate the naturalness problems, as can happen in the \ESSM
\cite{King:2005jy,King:2005my,King:2007uj,Athron:2010zz}, USSM
\cite{Fayet:1977yc,Suematsu:1994qm,Cvetic:1995rj,deCarlos:1997yv,Cvetic:1997ky,Demir:1998dk,Langacker:1998tc,Erler:2002pr,Choi:2006fz,Ham:2007wc,Langacker:2008yv,Ham:2008xf,Kalinowski:2008iq} or from other gauge extensions \cite{Batra:2003nj, Medina:2009ey, Bharucha:2013ela}, 
by raising the tree level Higgs mass. At the same time they can also
motivate models that are developed with a fresh perspective, based on
other considerations.  In both cases exploration of such models can be
aided if it is possible to quickly create a fast spectrum generator.
Currently there is only one option for this, a SPheno-like FORTRAN
code which can be generated from \sarah
\cite{Staub:2010ty,Staub:2009bi,Staub:2010jh,Staub:2012pb,Staub:2013tta}.

@@

%\cite{Kalinowski:2008iq}
\bibitem{Kalinowski:2008iq} 
  J.~Kalinowski, S.~F.~King and J.~P.~Roberts,
  %``Neutralino Dark Matter in the USSM,''
  JHEP {\bf 0901}, 066 (2009)
  [arXiv:0811.2204 [hep-ph]].
  %%CITATION = ARXIV:0811.2204;%%
  %30 citations counted in INSPIRE as of 09 Jun 2014
%\cite{Bharucha:2013ela}

\bibitem{Bharucha:2013ela} 
  A.~Bharucha, A.~Goudelis and M.~McGarrie,
  %``En-gauging Naturalness,''
  arXiv:1310.4500 [hep-ph].
  %%CITATION = ARXIV:1310.4500;%%
  %9 citations counted in INSPIRE as of 12 Jun 2014

%\cite{Batra:2003nj}
\bibitem{Batra:2003nj} 
  P.~Batra, A.~Delgado, D.~E.~Kaplan and T.~M.~P.~Tait,
  %``The Higgs mass bound in gauge extensions of the minimal supersymmetric standard model,''
  JHEP {\bf 0402}, 043 (2004)
  [hep-ph/0309149].
  %%CITATION = HEP-PH/0309149;%%
  %174 citations counted in INSPIRE as of 12 Jun 2014
%\cite{Medina:2009ey}
\bibitem{Medina:2009ey} 
  A.~D.~Medina, N.~R.~Shah and C.~E.~M.~Wagner,
  %``A Heavy Higgs and a Light Sneutrino NLSP in the MSSM with Enhanced SU(2) D-terms,''
  Phys.\ Rev.\ D {\bf 80}, 015001 (2009)
  [arXiv:0904.1625 [hep-ph]].
  %%CITATION = ARXIV:0904.1625;%%
  %9 citations counted in INSPIRE as of 12 Jun 2014
